Efficiently Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-13 robdml.tex
tex

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}

@@

\[
	\big(1-\frac{\text{Clip}_0^{U_L}[l_{t-1}]}{U_L} \big)\times
	(U_H + (H_D - H_S).relu())
\]

@@

To validate the effectiveness of our proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200~\cite{cub200}, Cars-196~\cite{cars196},
and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
for ease of comparison.
%
The setup is also consistent to standard DML~\cite{revisiting}.

@@

\subsection{Selection of Source/Destination Hardness}

@@

In literature, a series of triplet sampling strategies exist, such as random,
semi-hard~\cite{facenet}, soft-hard[], distance[], and hardest sampling.
%
Any of these can be selected for source triplet and destination triplet.

@@

@@

\oo{experiment, 8 step by default}
Number of PGD Steps $\eta$.
\cref{fig:introplot}

@@

@@

>>>>

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}
\usepackage{colortbl}

@@

\[
	\big(1-\text{Clip}_0^{U_L}[l_{t-1}]/U_L \big)\times
	U_H
\]

@@

To validate the effectiveness of our proposed defense, we conduct experiments
on three commonly used DML datasets: CUB-200-2011~\cite{cub200}, Cars-196~\cite{cars196},
and Stanford-Online-Products (SOP)~\cite{sop}.
%
We follow the same experiment setup of the state-of-the-art work~\cite{robrank}
for ease of comparison.
%
The setup is also consistent to standard DML~\cite{revisiting}.

@@

\subsection{Selection of Source \& Destination Hardness}

@@

% 1. possible combinations

In literature, various triplet sampling strategies exist, such as random,
semihard~\cite{facenet}, softhard[], distance~\cite{distance}, and the hardest negative sampling
(\ie, the negative sample with the largest loss value).
%
Although any of them can be selected for source or destination hardness for HM,
not all the possible combinations are expected to be effective or efficient.
%
In order to figure out an empirically good combination of source and destination
hardness, we adversarially train models on the CUB-200-2011 dataset with
every possible combination, and compare their R@1 and ERS performance in
\cref{tab:desth}.

% 2. hypothesis

@@

\subsection{Effectiveness of HM}

HM + different pgditer
CUB, 2 4 8 16 32

8; empirically selected as the base for further ablation study.

\oo{experiment, 8 step by default}

\subsection{Effectiveness of GA}

\subsection{Effectiveness of ICS}

@@

CUB 8 32

CARS 8 32

SOP 8 32

Number of PGD Steps $\eta$.
\cref{fig:introplot}

@@

(optional) ICS for ACT?

@@

\oo{In potential of future works}
Deep metric learning on adversarial example is also used for improving
adversarial robustness for deep classifiers~\cite{mao2019metric}.
